Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-19 resex.tex
Revised section on transverse damper (including figures).

\begin{figure*}
	\centering
	damper not active\\
	\begin{minipage}[t]{0.32\linewidth}
		\centering
	random excitation V, 2017\\
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		7th~turn V, 2017 exp.\\
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_v7th_no_damper_no_text.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		$10^{\mathrm{th}}$~turn V, 2016 exp.\\
		\includegraphics[height=0.75\linewidth]{2016_emitv_avg_rel_v10th_no_damper_no_text.png}
	\end{minipage}	
	damper active\\
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		random excitation V, 2017 exp.\\
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_vran_with_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		7th~turn V, 2017 exp.\\
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_v7th_with_damper_no_text.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		$10^{\mathrm{th}}$~turn V, 2016 exp.\\
		\includegraphics[height=0.75\linewidth]{2016_emitv_avg_rel_v10th_with_damper_no_text.png}
	\end{minipage}	
	\caption{\label{fig:damp} Relative intensity for bunches with transverse damper not active (top) and transverse damper active (bottom) for a random excitation only in V (left) and for 7th- (center) and \tenthtp\ only in V (right).}
\end{figure*}

>>>>

\begin{figure*}
  \begin{tabular}{ccc}
    \hline
    \multicolumn{3}{c}{Transverse damper off} \\ \hline
    Random excitation, V (2017) & \seventhtp, V (2017) & \tenthtp, V
                                                         (2016) \\
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_vran_no_damper.png}&
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_v7th_no_damper_no_text.png} &
    \includegraphics[width=\thirdwidth]{2016_emitv_avg_rel_v10th_no_damper_no_text.png}\\
    \hline
    \multicolumn{3}{c}{Transverse damper active} \\ \hline
    Random excitation, V (2017) & \seventhtp, V (2017) & \tenthtp, V
                                                         (2016) \\
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_vran_with_damper.png} &
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_v7th_with_damper_no_text.png} &
    \includegraphics[width=\thirdwidth]{2016_emitv_avg_rel_v10th_with_damper_no_text.png} \\
    \end{tabular}
    \caption{Comparison of measured vertical emittances for bunches
      with transverse damper off (top row) and with transverse damper
      on (bottom row), during random V excitations (left), \seventhtp\
      in V (center) and \tenthtp\ in V (right). (Because of a change
      in experimental setup, for the bunches represented by the yellow
      line in the bottom right plot, the excitation was zero instead
      of the maximum value.)}
    \label{fig:damp}
\end{figure*}
